%-------------------------
% Resume Written in LateX
% Author : Kenneth (Alex) Jenkins
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage{amsmath}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Kenneth Alexander Jenkins} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:4703178338}{+14703178338}
    $|$
    \faAt \hspace{.5pt} \href{mailto:kajenkins100@gmail.com}{kajenkins100@gmail.com}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/rockenman1234}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{https://alexj.io}{Portfolio}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/Georgia+Institute+of+Technology/@33.7756178,-84.396285,15z/data=!4m6!3m5!1s0x88f5048aebc34fe3:0xb52ad03e3ad8c50f!8m2!3d33.7756178!4d-84.396285!16zL20vMGYxbmw}{Atlanta, Georgia}
    $|$
    \text{\faFlag} U.S. Citizen
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {Georgia Institute of Technology
      % \normalfont{(Admission rate: 0.85\%)}
      }{Atlanta, Georgia}
      {B.Sc. in Computer Engineering; Fall 2024 \textbf{HOPE GPA: 3.65/4.00}}{May 2022 \textbf{--} December 2026 (Expected)}
      {Concentrations: Cyber Security, \& Systems/Architecture}
      {}
    
    \resumeSubheading
      {New Creation Christian Academy 
      % \normalfont{(Admission rate: 0.85\%)}
      }{McDonough, Georgia}
      {High School Diploma; Cum Laude \textbf{GPA: 3.95/4.00}}{August 2018 \textbf{--} May 2022}
    
  \resumeSubHeadingListEnd






%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

\resumeSubheading
    {Turbine Logic}{Atlanta, Georgia}
    {Engineering Analyst Intern}{January 2025 \textbf{--} Present}
    \resumeItemListStart
    \resumeItem{Supported the implementation and certification of cybersecurity requirements, including compliance with government standards and other industry regulations, to enhance the organization's security posture.}
    \resumeItem{Designed and deployed a custom secure server for business operations, utilizing Red Hat Enterprise Linux (RHEL) to ensure robust system reliability, security, and performance.}
    \resumeItem{Collaborated with cross-functional teams to assess cybersecurity risks and develop mitigation strategies, enhancing protection against potential vulnerabilities and threats.}
    \resumeItem{Contributed to technical documentation for server configurations, security policies, and compliance procedures to support ongoing audits and certification processes.}
    \resumeItemListEnd

      \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, Georgia}
      {Undergraduate Teaching Assistant – Art \& Generative AI}{January 2025 \textbf{--} Present}
        \resumeItemListStart
            \resumeItem{Collaborated with the instructor to prepare lesson materials and deliver engaging content on Art \& Generative AI.}
            \resumeItem{Provided individualized support to students through office hours, email correspondence, and additional resources to ensure comprehension of course concepts.}
            \resumeItem{Conducted study sessions to reinforce key topics and facilitate collaborative learning among students.}
            \resumeItem{Developed code implemented for instructional use during the second half of the semester, demonstrating practical applications of Generative AI techniques.}
        \resumeItemListEnd

\resumeSubheading
    {Valmet, Inc.}{Atlanta, Georgia}
    {DevOps \& Automation Engineering Intern}{May 2024 \textbf{--} December 2024}
    \resumeItemListStart
    \resumeItem{Collaborated with industry-leading experts in the Pulp \& Paper sector to support customer sales planning, goal alignment, and mill audit processes.}
    \resumeItem{Designed and implemented an AI-powered tool written in Go, using Retrieval-Augmented Generation (RAG) to streamline internal documentation workflows; with significant potential to reduce operational costs by up to \$30 million annually.}
    \resumeItem{Developed a Python-based tool to enhance cybersecurity and operational efficiency by automating vulnerability scanning, verifying antivirus functionality, and ensuring proper system security configurations, saving IT engineers hours of weekly setup time.}
    \resumeItem{Created an internal software solution to monitor and manage KPIs for industrial process measurements, improving operational efficiency and saving an estimated \$100,000 annually.}
    \resumeItem{Diagnosed a critical boiler-furnace camera issue during a mill audit, preventing costly delays and eliminating the need for international engineer travel, saving the company thousands of dollars.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Montra Technologies, Inc.}{Atlanta, Georgia}
      {IT Logistics Intern}{February 2024 \textbf{--} May 2024}
        \resumeItemListStart
        \resumeItem{Contributed to device logistics management, ensuring timely deployment and efficient resource utilization across different locations.}
        \resumeItem{Participated in device management efforts, ensuring devices were updated and ready for deployment while collaborating on security monitoring systems.}
        \resumeItem{Assisted in field rollout and installation procedures, facilitating smooth device setup and operation in various operational environments.}
        \resumeItem{Contributed to the development of features simplifying cyber compliance processes, ensuring adherence to cybersecurity standards and facilitating audits.}
        \resumeItemListEnd

  \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, Georgia}
      {Guest Services Manager}{October 2023 \textbf{--} August 2024}
        \resumeItemListStart
            \resumeItem{Managed event setup logistics, ensuring efficient arrangement of furniture across 75\% of Georgia Tech's most trafficked spaces.}
            \resumeItem{Collaborated with clients to fulfill their event requirements and conducted routine facility checks to address client needs and maintain facility standards.}
            \resumeItem{Facilitated seamless guest experiences by overseeing event preparations and addressing any facility-related issues promptly.}
        \resumeItemListEnd

    % \vspace{15pt}
    \resumeSubheading
      {Foster \& Smith, LLC}{Jonesboro, Georgia}
      {Law Clerk \& IT Supervisor}{November 2021 \textbf{--} January 2024}
        \resumeItemListStart
            \resumeItem{Researched and advised Attorneys on past and present legal cases, included archiving and managing legal documents.}
            \resumeItem{Developed Python and PHP programs for internal purposes, including a document creation tool for will drafting and a server-side application for document management.}
            \resumeItem{Built a stable computer server system for use in house. Developed remote access capabilities for the firm, and lead the transition to a new time management platform built for Attorneys.}
            \resumeItem{Managed and executed a meticulous multi-disk data recovery project, successfully restoring vital files from an obscure file system after a catastrophic data loss event. I then implemented a robust off-site backup strategy, incorporating nightly encrypted disk syncs with rsync to a BackBlaze data center in Virginia, ensuring both data integrity and compliance with all legal requirements.}
            \resumeItem{Implemented and maintained network infrastructure, including routers, switches, and firewalls - monitored traffic using wireshark packet analysis software to ensure secure connectivity and data flow.}
            \resumeItem{Conducted regular offsite data backups of all employee computers and disaster recovery planning, safeguarding critical legal documents through encryption and compression algorithms on local server ensuring business continuity.}
            \resumeItem{Implemented and enforced security protocols, including user authentication, access controls, and antivirus measures to protect sensitive client information.}
            \resumeItem{Researched, evaluated, and implemented Nextcloud as a cost-effective document management solution. Deployed and customized the server on FreeBSD, optimizing performance and aligning with branding. Strengthened security through Fail2ban, mitigating unauthorized access risks.}
        \resumeItemListEnd
    
    \resumeSubheading
      {Clayton State University}{Morrow, Georgia}
      {Undergraduate Teaching Assistant \textbf{--} Trigonometry and Analytical Geometry}{Jan 2023 \textbf{--} May 2023}
        \resumeItemListStart
            \resumeItem{Assisted the instructor in conducting Trigonometry classes by preparing lesson materials, explaining concepts to students, and conducting study sessions.}
            \resumeItem{Provided feedback to students on graded homework assignments and exams, and tracked their progress throughout the course.}
            \resumeItem{Supported students who were struggling with Trigonometry by providing extra help during office hours, answering questions via email, or referring them to additional resources.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Muse\textunderscore AI Research Group}{Georgia Institute of Technology}
    {Undergraduate Research Assistant}{August 2024 \textbf{--} Present}
    \resumeItemListStart
            \resumeItem{Created and deployed coding tutorials to support engineering education initiatives at Georgia Tech, enhancing and improving student learning outcomes with artifical inteligence.}
            \resumeItem{Developed a frontend UI aimed at establishing the program as the gold standard in AI-driven preformance art creation, released under a FOSS license.}
            \resumeItem{Collaborated with a multidisciplinary team to integrate EEG data from a brain-computer interface (BCI) into the creation of dynamic visual art and harmonic music, driven by live brainwave data for a performance.} $|$ \emph{\href{https://github.gatech.edu/kjenkins60/MUSE_Research_Group}{\color{blue}GitHub}}{}
    \resumeItemListEnd
  
    \resumeSubheading
      {Mathematics Research Projects}{Clayton State University}
      {Undergraduate Research Assistant}{August 2022 \textbf{--} May 2023}
        \resumeItemListStart
            \resumeItem{ Newtons Method \textbf{--} A Python program written to demonstrate Newton's Method of finding roots.} $|$ \emph{\href{https://github.com/rockenman1234/newtonsmethod}{\color{blue}GitHub}}{}
            \resumeItem{ Java Math Iterator \textbf{--} A Java program written to demonstrate computational iteration.} $|$ \emph{\href{https://github.com/rockenman1234/java_math_integrator}{\color{blue}GitHub}}{}
            \resumeItem{ Calculus Cruncher \textbf{--} A customizable math flashcard web app, featuring key terms and definitions.} $|$ \emph{\href{https://github.com/rockenman1234/Calculus_Cruncher}{\color{blue}GitHub}}{}
        \resumeItemListEnd
        
    \resumeSubheading
    {Arts Conference Presentations}{}
     {{\href{https://www.youtube.com/playlist?list=PLNIeiKhj4_QRKH-fXi5uLzfnXnkHhH3j4}{\color{Blue} GT Arts Exhibition}} \textbf{--} Georgia Institute of Technology}{October 2024}
    \resumeItemListStart
        \resumeItem{ Muse\textunderscore AI Research Group \textbf{--} Led the development of an innovative project integrating AI, neuroscience, and art into a seamless, interactive platform for live dance performances, utilizing the Muse 2, an affordable consumer-grade brain-computer interface (BCI).}
    \resumeItemListEnd
        \resumeSubheading
        {Research Conference Presentations}{} %This produces a blank line
        {{\href{https://github.com/rockenman1234/Capstone-Presentations/blob/main/Clayton_State_University/Metacognition/Manifest_SSC-2023.pdf}{\color{Blue} Student Success Conference}} \textbf{--} Clayton State University}{April 2023}
        \resumeItemListStart
            \resumeItem{ Falling Into Viscosity \textbf{--} This project aimed to determine the viscosity of an unknown fluid by analyzing a video of a falling metal ball. The motion was tracked using the Open-source Tracker video analysis software. The results demonstrated the effectiveness of combining Tracker software with Stokes law for measuring fluid viscosity, providing a low-cost and accessible method with potential applications in research and industry. } $|$ \emph{\href{https://github.com/rockenman1234/Capstone-Presentations/blob/main/Clayton_State_University/Viscosity/Falling_Into_Viscosity.pdf}{\color{blue}View Poster}}{}
            
            \resumeItem{ Developing Metacognitive Skills \textbf{--} This project aimed to examine the impact of developing metacognitive planning skills on student success in online math classes. The objective was to contribute to the research on metacognition in virtual learning environments and provide insights for educators and students in developing effective metacognitive strategies for online learning.} $|$ \emph{\href{https://github.com/rockenman1234/Capstone-Presentations/blob/main/Clayton_State_University/Metacognition/Developing_Metacognitive_Skills(CSU).pdf}{\color{blue} View Poster}}{}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd


%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{National Hispanic Scholar:}{ Merit-based award for Hispanic students pursuing a college degree. Includes financial support, Scholar Support Services (mentoring, leadership development, personal wellness training), and additional support for demonstrated financial need. Awarded to less than 10K high-school students per year.} \\ \vspace{3pt}
        
        \textbf{AP Scholar Award:}{ Awarded to high-school seniors who receive scores of 3 or higher on three or more AP Exams.} \\ \vspace{3pt}
        
        \textbf{Crusader Award:}{ The highest honor given to athletes at NCCA, presented to one varsity athlete who demonstrate exceptional character, leadership, work ethic, discipline, accountability, and positive influence on their teammates.} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd



%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
        {\textbf{Argon} $|$ \emph{\href{https://github.com/rockenman1234/Argon2}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{A open-source GUI application designed to provide a stable and reliable platform for software developers and power users to get started using their Mac's as quickly and reliably as possible - without leaving a trace.}
            \resumeItem{Written in Go and Shell.}
          \resumeItemListEnd
    
      
      \resumeProjectHeading
        {\textbf{FerrumCrimper} $|$ \emph{\href{https://github.com/rockenman1234/FerrumCrimper}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{A Rust CLI tool for efficient file management, compression, and archival with support for multiple formats and secure data handling. }
            \resumeItem{Played a founding role in the development of a highly successful online resource, which has been downloaded/ accessed over 1,000 times by users worldwide.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Buzz\_Off} $|$ \emph{\href{https://github.com/rockenman1234/Buzz_off}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{A browser extension that replaces any text related to The university Of Georgia with various taunts.}
            \resumeItem{After publication, it was viewed over 74K times in under 72 hours -- it currently has over 50+ active users.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Fedora Tweaks} $|$ \emph{\href{https://github.com/rockenman1234/fedora-tweaks}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{A Bash script that is designed to make the RHEL based Fedora Linux distribution, more usable and user friendly as quickly as possible.}
            \resumeItem{The script has been used hundreds of times, and was forked into a larger repository of Linux scripts.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming:}{ Java, Python, Rust, C, C++, C\#, Go, JavaScript, TypeScript, HTML, CSS, PHP, Shell, Swift, Verilog, VHDL, x86/MIPS/RISC-V Assembly} \\ \vspace{3pt}
        
        \textbf{Technologies:}{ Git, Arduino, Linux, Berkeley Software Distributions (BSD), Data Recovery, Digital forensics, Reverse Engineering } \\ \vspace{3pt}
        
        \textbf{Developer Tools}{: IDA Pro, Ghidra, Android Studio, Wireshark, Altera Quartus, NI LabVIEW, Apple XCode} \\
        \vspace{3pt}

        \textbf{Languages:}{ English (Native), Spanish (Professional)} \\
        \vspace{3pt}

        \textbf{Frameworks}{: React, Fyne, Ollama, Metal, Node.js, Django} \\
        % \textbf{Libraries}{: X, X, X} \\
        % \textbf{Applications}{: X, X, X}
    }}
  \resumeSubHeadingListEnd

%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Business Skills, Data and Digital Skills, Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

\section{Organizations}
  \resumeSubHeadingListStart
    
    \resumeOrganizationHeading
     {Institute of Electrical and Electronics Engineers (IEEE)}{May 2023 -- Present}{Student Member} \\
     \vspace{3pt}
    
  \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Swimming, Fitness, Eight-ball}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

\section{References}
  \resumeSubHeadingListStart
      \resumeOrganizationHeading
      {Travis Smith -- Attorney at Law}{TSmith@fostersmith.law}{Foster \& Smith, LLC -- Former Employer and Supervisor}

      \resumeOrganizationHeading
      {Dr. Francesco Fedele -- Professor, College of Engineering}{
fedele@gatech.edu}{Georgia Institute of Technology -- Former Instructor of Record, and Faculty/Research Supervisor}

      \resumeOrganizationHeading
      {Dr. Christopher Raridan -- Professor of Mathematics}{ChristopherRaridan@clayton.edu}{Clayton State University -- Former Faculty Supervisor and Research Advisor}{Clayton State University}
  
      \resumeOrganizationHeading
      {Jelinda Spotorno -- Senior Lecturer of Mathematics}
      {JelindaSpotorno@clayton.edu}{Clayton State University -- Former Instructor of Record and Faculty Supervisor}
      
  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
